---
title: "Answers"
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Answers for ExerciseSheet 3

#### 1 d)
Strength of git:
It allows for version control, where the development proccess is split up into different versions, allowing for rollback onto a previous version.
It also allows for (asynchronous) collaboration with branches.

Weaknesses:
Character limit in the commit messages limits the maximum complexity of the commit
Branches, merge-conflicts, and other git aspects technically increase the complexity of the task, as it adds on top of the actual programming task.

### 3
#### a)
```{r setup, echo=TRUE}
pixarFilms <- read.csv("pixar_films.csv")
#for debug:
colnames(pixarFilms)

pixarFilms <- pixarFilms[!is.na(pixarFilms$film) & pixarFilms$film != "", ]

unique(pixarFilms$film_rating)
#the film rating says, what the minimum age requirement is for watching the movie
pixarFilms$film_rating <- factor(pixarFilms$film_rating,
                                  levels = c("G", "PG", "N/A"),
                                  ordered = TRUE)
#It makes sense, as one rating includes and overranks other, previous ratings.
```

#### b)
```{r setup, echo=TRUE}
#all unique titles
unique(pixarFilms$film)
#Series
#The Incredibles (1 and 2), Cars (1, 2 and 3), Toy Story (1, 2, 3 and 4), potentially also "Monsters, Inc." and "Monsters University", but unsure if they count. The same issue is with "Finding Nemo" and "Funding Dory", and also with "Lightyear" and the Toy Story Series, but that one I will ignore due to the radical difference.

#new column
pixarFilms$series <- NA

#manual assignement based on title structure
pixarFilms$series[grepl("Toy Story", pixarFilms$film)] <- "Toy Story"
pixarFilms$series[grepl("Cars", pixarFilms$film)] <- "Cars"
pixarFilms$series[grepl("Finding", pixarFilms$film)] <- "Finding"
pixarFilms$series[grepl("Monsters", pixarFilms$film)] <- "Monsters"
pixarFilms$series[grepl("Incredibles", pixarFilms$film) | grepl("The Incredibles", pixarFilms$film)] <- "The Incredibles"

#Series Dataframe and Summary
pixarFilmsSeries <- subset(pixarFilms, !is.na(series))

library(dplyr)
pixarFilmsSeriesSummary <- pixarFilmsSeries %>%
  group_by(series) %>%
  summarise(
    numberOfFilms = n(),
    filmTitles = paste(film, collapse = "; ")
  ) %>%
  arrange(desc(numberOfFilms))

#printing the Summary
print(pixarFilmsSeriesSummary)
```
