---
title: "Answers"
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Answers for ExerciseSheet 3

#### 1 d)
Strength of git:
It allows for version control, where the development proccess is split up into different versions, allowing for rollback onto a previous version.
It also allows for (asynchronous) collaboration with branches.

Weaknesses:
Character limit in the commit message title limits the maximum complexity of the commit, however, the description does not have a limit
Branches, merge-conflicts, and other git aspects technically increase the complexity of the task, as it adds on top of the actual programming task.

### 3
#### a)
```{r setup, echo=TRUE}
pixarFilms <- read.csv("pixar_films.csv")
#for debug:
colnames(pixarFilms)

pixarFilms <- pixarFilms[!is.na(pixarFilms$film) & pixarFilms$film != "", ]

unique(pixarFilms$film_rating)
#the film rating says, what the minimum age requirement is for watching the movie
pixarFilms$film_rating <- factor(pixarFilms$film_rating,
                                  levels = c("G", "PG", "N/A"),
                                  ordered = TRUE)
#It makes sense, as one rating includes and overranks other, previous ratings.
```

#### b)
```{r setup, echo=TRUE}
#all unique titles
unique(pixarFilms$film)
#Series
#The Incredibles (1 and 2), Cars (1, 2 and 3), Toy Story (1, 2, 3 and 4), potentially also "Monsters, Inc." and "Monsters University", but unsure if they count. The same issue is with "Finding Nemo" and "Funding Dory", and also with "Lightyear" and the Toy Story Series, but that one I will ignore due to the radical difference.

#new column
pixarFilms$series <- NA

#manual assignement based on title structure
pixarFilms$series[grepl("Toy Story", pixarFilms$film)] <- "Toy Story"
pixarFilms$series[grepl("Cars", pixarFilms$film)] <- "Cars"
pixarFilms$series[grepl("Finding", pixarFilms$film)] <- "Finding"
pixarFilms$series[grepl("Monsters", pixarFilms$film)] <- "Monsters"
pixarFilms$series[grepl("Incredibles", pixarFilms$film) | grepl("The Incredibles", pixarFilms$film)] <- "The Incredibles"

#Series Dataframe and Summary
pixarFilmsSeries <- subset(pixarFilms, !is.na(series))

library(dplyr)
pixarFilmsSeriesSummary <- pixarFilmsSeries %>%
  group_by(series) %>%
  summarise(
    numberOfFilms = n(),
    filmTitles = paste(film, collapse = "; ")
  ) %>%
  arrange(desc(numberOfFilms))

#printing the Summary
print(pixarFilmsSeriesSummary)
```
#### c)
```{r, echo=TRUE}
publicResponse <- read.csv("public_response.csv")
publicResponse
unique(publicResponse$cinema_score)
#while there are only A, A+ and A-, I will follow this pattern futher down for consistency
scoreGrades <- c("F", "F+", "D-", "D", "D+", "C-", "C", "C+", "B-", "B", "B+", "A-", "A", "A+")

publicResponse$cinema_score <- factor(publicResponse$cinema_score,
                                       levels = scoreGrades,
                                       ordered = TRUE)

#left-merging with common key "film"
pixarFilmsScoresCombined <- merge(pixarFilms, publicResponse, by = "film", all.x = TRUE)

```

#### d)
```{r, echo=TRUE}
#I chose rotten tomatoes for the graph, as it represents the opinion of the general audience, especially more so than cinema_score or critics_choice
library(ggplot2)
seriesFilmsScoresCombined <- pixarFilmsScoresCombined %>%
  filter(!is.na(series)) %>%
  arrange(series, release_date)
#ordered after release date
seriesFilmsScoresCombined <- seriesFilmsScoresCombined %>%
  mutate(orderedData = factor(film, levels = film[order(series, release_date)]))

ggplot(seriesFilmsScoresCombined, aes(x = series, y = rotten_tomatoes, fill = orderedData)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.8) +
  labs(
    title = "Rotten Tomatoes Scores for Pixar Film Series",
    x = "Pixar Film Series",
    y = "Rotten Tomatoes Score (%)",
    fill = "Film"
  )
#Generally, the sequels are rated lower than the first movies except for one clear outlier: Cars 2, which is rated significantly lower than its sequel.
```

### 4
#### c)
Dataset Name: "German road deaths and accidents - destatis"

Link: https://github.com/owid/owid-datasets/blob/master/datasets/German%20road%20deaths%20and%20accidents%20-%20destatis/German%20road%20deaths%20and%20accidents%20-%20destatis.csv

#### d)
Did advancements in technology lead to both safer and in total less accidents over the years?

#### e)
```{r, echo=TRUE}
GermanAccidents = read.csv("German road deaths and accidents - destatis.csv")
#additionally taking a population into account
GermanPopulation = read.csv("Germany-Population-Population-2025-06-05-20-14.csv", sep = ";")

GermanPopulation <- GermanPopulation %>%
  rename(Year = X)
#leftjoin the Population to the accidents
combinedAccidentsPop <- left_join(GermanAccidents, GermanPopulation, by = "Year")

#filtering and cleaning
GermanAccidentsCleaned <- combinedAccidentsPop %>%
  select(Year, Accidents.reported.to.police, Road.deaths, Road.injuries, Population) %>%
  filter(!is.na(Year), !is.na(Accidents.reported.to.police), !is.na(Road.deaths), !is.na(Road.injuries), !is.na(Population))

#relativising the data, number of Deaths and Injuries relative to the number of accidents, and the number of accidents relativised to population that year
relativisedGermanAccidentsCleaned <- GermanAccidentsCleaned %>%
  mutate(
    deathsPerAccident = Road.deaths / Accidents.reported.to.police,
    injuriesPerAccident = Road.injuries / Accidents.reported.to.police,
    accidentsPer100kPop = (Accidents.reported.to.police / Population) * 100000
  )


#correlation between year, which I use as the metric for the technological level, and the amount of crashes per 100k Pop.
correlation <- cor(relativisedGermanAccidentsCleaned$Year, relativisedGermanAccidentsCleaned$accidentsPer100kPop)
print(correlation)
#there is a positive correlation between the year and the amount of crashes per 100k Pop, but that could be attributed to the higher amount of road vehicles on the road, and the relative affordability/accessibility of cars

deathModel <- lm(deathsPerAccident ~ Year, data = relativisedGermanAccidentsCleaned)
injuriesModel <- lm(injuriesPerAccident ~ Year, data = relativisedGermanAccidentsCleaned)
library(easystats)
report(deathModel)
report(injuriesModel)

#Both deaths and injuries show a strong and statistically significant decline over time, with more than 88% of the variance explained by the year. This trend supports the hypothesis, that the technological advancements (and improvements to the overall system, such as better medical treatments) make traffic accidents progressively less deadly and less prone to injuries over the past decades in Germany.
```


