---
title: "Answers"
output: html_document
date: "2025-06-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Answers for ExerciseSheet 3

#### 1 d)
Strength of git:
It allows for version control, where the development proccess is split up into different versions, allowing for rollback onto a previous version.
It also allows for (asynchronous) collaboration with branches.

Weaknesses:
Character limit in the commit messages limits the maximum complexity of the commit
Branches, merge-conflicts, and other git aspects technically increase the complexity of the task, as it adds on top of the actual programming task.

### 3
#### a)
```{r setup, echo=TRUE}
pixarFilms <- read.csv("pixar_films.csv")
#for debug:
colnames(pixarFilms)

pixarFilms <- pixarFilms[!is.na(pixarFilms$film) & pixarFilms$film != "", ]

unique(pixarFilms$film_rating)
#the film rating says, what the minimum age requirement is for watching the movie
pixarFilms$film_rating <- factor(pixarFilms$film_rating,
                                  levels = c("G", "PG", "N/A"),
                                  ordered = TRUE)
#It makes sense, as one rating includes and overranks other, previous ratings.
```